MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-03-25 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix input

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(R.utils)
library(ggplot2)
library(limma)
library(psych)
library(edgeR)
library(cqn)
library(lme4)
library(biomaRt)
#devtools::install_github("GabrielHoffman/variancePartition@613dfe9")
library(variancePartition)
library(synapser)
library(knitr)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='add-dream')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21071622'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

>>>>

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(R.utils)
library(ggplot2)
library(limma)
library(psych)
library(edgeR)
library(cqn)
library(lme4)
library(biomaRt)
library(variancePartition)
library(synapser)
library(knitr)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='add-dream')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21754352'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL
